visualizemi: Visualization, Effect Size, and Replication of Measurement Invariance for Registered Reports

### 2023-10-17 manuscript.tex
making figures

The output from this function are several \emph{ggplot2} objects that can be edited or saved directly using \emph{ggplot2} functionality (Wickham, 2016).

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  \texttt{saved\_configural}: a saved fitted model at the configural level with no equality constraints. This model should include all other \emph{lavaan} settings you would like to use, such as \texttt{estimator} or \texttt{ordered}.
\end{enumerate}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 126,722.491 & 126,888.707 & 0.934 & 0.923 & 0.094 & 0.036\\
Group Clinical & 52,961.421 & 53,099.720 & 0.919 & 0.904 & 0.090 & 0.044\\
Group Student & 69,100.985 & 69,254.310 & 0.928 & 0.915 & 0.108 & 0.035\\
Configural & 122,118.406 & 122,617.055 & 0.926 & 0.912 & 0.102 & 0.036\\
loadings & 122,144.532 & 122,566.010 & 0.925 & 0.918 & 0.098 & 0.043\\
intercepts & 122,544.109 & 122,888.415 & 0.911 & 0.910 & 0.103 & 0.052\\
residuals & 126,466.241 & 126,727.438 & 0.780 & 0.793 & 0.156 & 0.086\\
\bottomrule
\end{tabular}

@@

By examining our estimates, we can see that item seven on the RS-14 is estimated at nearly 5 points for the clinical sample, while the student sample has a lower mean around 4.5 points. Generally, students show higher means on the items of the RS14, but when all loadings and other intercepts are constrained to be equal, and this one item is relaxed, this pattern flips so that clinical groups show higher item intercepts. Given the scale is a 1-7 Likert type scale, .5 a point represents a potentially sizable change on the scale. Item seven covers perseverance after hardship, and all items can be found in the user manual for the scale at www.resiliencecenter.com. The effect size from \(d_{MACS}\) suggests a small to medium effect, 0.28. In this next code section, we repeat this process for the RS6, as the CFI for our model with only RS7 does not achieve the levels of partial invariance for our \(\Delta\)CFI criterion (i.e., \textless= .01 downward change in fit: metric CFI = .925, partial scalar CFI = .914). See Figure \ref{fig:rs7-img} for the difference between item intercepts and latent means.

@@

Next, we would examine the strength of the effects of replication on each parameter at the intercept level. By examining \ref{tab:table-boot-effects}, it is clear that most of the item means are unlikely to replicate, even though two particular items can be used to create partial invariance. Figures \ref{fig:rs-partial-pic} and \ref{fig:rs-partial-pic2} display the three plots provided in the \texttt{bootstrap\_partial()} function. In general, we should expect \(M_{D}\) = 0.23 when items are invariant and \(M_{D}\) = 0.26 when items are not invariant. The effect size of non-invariant items ranges from 0.43 to 0.62.

@@

\begin{tabular}{lllllll}
\toprule
term & \multicolumn{1}{c}{non\_invariant} & \multicolumn{1}{c}{random\_non\_invariant} & \multicolumn{1}{c}{h\_nmi} & \multicolumn{1}{c}{h\_mi} & \multicolumn{1}{c}{h\_nmi\_p} & \multicolumn{1}{c}{h\_mi\_p}\\
\midrule
RS \textasciitilde{}1 & 0.991 & 0.007 & 2.784 & -2.784 & 0.886 & -0.886\\
RS1 \textasciitilde{}1 & 0.989 & 0.007 & 2.764 & -2.764 & 0.880 & -0.880\\
RS10 \textasciitilde{}1 & 0.988 & 0.007 & 2.755 & -2.755 & 0.877 & -0.877\\
RS11 \textasciitilde{}1 & 0.991 & 0.007 & 2.784 & -2.784 & 0.886 & -0.886\\
RS12 \textasciitilde{}1 & 0.991 & 0.007 & 2.784 & -2.784 & 0.886 & -0.886\\
RS13 \textasciitilde{}1 & 0.991 & 0.007 & 2.784 & -2.784 & 0.886 & -0.886\\
RS14 \textasciitilde{}1 & 0.990 & 0.007 & 2.774 & -2.774 & 0.883 & -0.883\\
RS2 \textasciitilde{}1 & 0.985 & 0.007 & 2.728 & -2.728 & 0.869 & -0.869\\
RS3 \textasciitilde{}1 & 0.988 & 0.007 & 2.755 & -2.755 & 0.877 & -0.877\\
RS4 \textasciitilde{}1 & 0.990 & 0.007 & 2.774 & -2.774 & 0.883 & -0.883\\
RS5 \textasciitilde{}1 & 0.984 & 0.007 & 2.720 & -2.720 & 0.866 & -0.866\\
RS6 \textasciitilde{}1 & 0.979 & 0.007 & 2.683 & -2.683 & 0.854 & -0.854\\
RS7 \textasciitilde{}1 & 0.974 & 0.007 & 2.650 & -2.650 & 0.844 & -0.844\\
RS8 \textasciitilde{}1 & 0.991 & 0.007 & 2.784 & -2.784 & 0.886 & -0.886\\
RS9 \textasciitilde{}1 & 0.987 & 0.007 & 2.746 & -2.746 & 0.874 & -0.874\\
\bottomrule
\end{tabular}

@@

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/rs-partial-pic-1.pdf}
\caption{\label{fig:rs-partial-pic}RS14 scale invariance for item intercepts. The left panel indicates the raw score difference between groups and items, while the right panel indicates the effect size for group differences based on invariance.}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/rs-partial-pic2-1.pdf}
\caption{\label{fig:rs-partial-pic2}RS14 scale invariance density plots, illustrating invariant versus non-invariant bootstrapped and random runs for each parameter.}
\end{figure}

@@

\hypertarget{simulating-from-models}{%
\subsection{Simulating from models}\label{simulating-from-models}}

@@

\hypertarget{simulating-from-matrices}{%
\subsection{Simulating from matrices}\label{simulating-from-matrices}}

@@

\hypertarget{mgcfa-model-fit-statistics}{%
\subsection{MGCFA Model Fit Statistics}\label{mgcfa-model-fit-statistics}}

Model fit statistics are provided for each of the ten model combinations (invariant, three sizes for each ladings, intercepts, and residuals). These tables could be used to examine the traditional change in fit statistics cutoff rules of thumb (Cheung \& Rensvold, 2002), such as \(\Delta\) CFI or \(\Delta\) RMSEA, to the visualizations presented in the manuscript.

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,516.454 & 7,579.673 & 1.000 & 1.036 & 0.000 & 0.006\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,767.599 & 3,820.421 & 1.000 & 1.008 & 0.000 & 0.021\\
Configural & 7,533.348 & 7,659.786 & 0.991 & 0.982 & 0.030 & 0.026\\
loadings & 7,528.476 & 7,638.056 & 0.994 & 0.992 & 0.020 & 0.033\\
intercepts & 7,522.397 & 7,615.118 & 1.000 & 1.003 & 0.000 & 0.035\\
residuals & 7,520.435 & 7,592.083 & 0.991 & 0.992 & 0.020 & 0.046\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,530.321 & 7,593.540 & 0.977 & 0.955 & 0.049 & 0.025\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,785.242 & 3,838.064 & 0.979 & 0.958 & 0.050 & 0.029\\
Configural & 7,550.991 & 7,677.430 & 0.978 & 0.956 & 0.048 & 0.030\\
loadings & 7,550.133 & 7,659.713 & 0.966 & 0.952 & 0.051 & 0.047\\
intercepts & 7,542.675 & 7,635.397 & 0.979 & 0.977 & 0.035 & 0.047\\
residuals & 7,534.091 & 7,605.739 & 0.993 & 0.994 & 0.019 & 0.054\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,598.681 & 7,661.900 & 0.946 & 0.893 & 0.078 & 0.035\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,820.090 & 3,872.912 & 0.969 & 0.938 & 0.067 & 0.034\\
Configural & 7,585.839 & 7,712.277 & 0.972 & 0.944 & 0.058 & 0.033\\
loadings & 7,613.434 & 7,723.014 & 0.865 & 0.807 & 0.107 & 0.079\\
intercepts & 7,606.648 & 7,699.370 & 0.874 & 0.860 & 0.091 & 0.079\\
residuals & 7,600.057 & 7,671.705 & 0.880 & 0.895 & 0.079 & 0.091\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,684.982 & 7,748.201 & 0.987 & 0.973 & 0.040 & 0.023\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,857.143 & 3,909.965 & 0.992 & 0.984 & 0.037 & 0.029\\
Configural & 7,622.892 & 7,749.330 & 0.986 & 0.972 & 0.042 & 0.030\\
loadings & 7,674.188 & 7,783.767 & 0.817 & 0.738 & 0.131 & 0.095\\
intercepts & 7,667.682 & 7,760.403 & 0.824 & 0.805 & 0.113 & 0.096\\
residuals & 7,683.177 & 7,754.825 & 0.762 & 0.793 & 0.116 & 0.138\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,520.471 & 7,583.690 & 1.000 & 1.035 & 0.000 & 0.007\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,767.599 & 3,820.421 & 1.000 & 1.008 & 0.000 & 0.021\\
Configural & 7,533.348 & 7,659.786 & 0.991 & 0.982 & 0.030 & 0.026\\
loadings & 7,528.476 & 7,638.056 & 0.994 & 0.992 & 0.020 & 0.033\\
intercepts & 7,526.312 & 7,619.034 & 0.987 & 0.986 & 0.027 & 0.040\\
residuals & 7,524.356 & 7,596.005 & 0.975 & 0.978 & 0.033 & 0.050\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,538.375 & 7,601.594 & 1.000 & 1.033 & 0.000 & 0.008\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,767.599 & 3,820.421 & 1.000 & 1.008 & 0.000 & 0.021\\
Configural & 7,533.348 & 7,659.786 & 0.991 & 0.982 & 0.030 & 0.026\\
loadings & 7,528.476 & 7,638.056 & 0.994 & 0.992 & 0.020 & 0.033\\
intercepts & 7,544.002 & 7,636.724 & 0.917 & 0.907 & 0.068 & 0.059\\
residuals & 7,542.064 & 7,613.712 & 0.905 & 0.917 & 0.065 & 0.067\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,568.748 & 7,631.967 & 1.000 & 1.032 & 0.000 & 0.008\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,767.599 & 3,820.421 & 1.000 & 1.008 & 0.000 & 0.021\\
Configural & 7,533.348 & 7,659.786 & 0.991 & 0.982 & 0.030 & 0.026\\
loadings & 7,528.476 & 7,638.056 & 0.994 & 0.992 & 0.020 & 0.033\\
intercepts & 7,574.054 & 7,666.776 & 0.797 & 0.775 & 0.106 & 0.084\\
residuals & 7,572.174 & 7,643.823 & 0.785 & 0.813 & 0.097 & 0.090\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,462.007 & 7,525.226 & 1.000 & 1.020 & 0.000 & 0.013\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,703.797 & 3,756.619 & 0.962 & 0.924 & 0.061 & 0.037\\
Configural & 7,469.546 & 7,595.984 & 0.969 & 0.938 & 0.054 & 0.034\\
loadings & 7,471.637 & 7,581.217 & 0.944 & 0.920 & 0.062 & 0.049\\
intercepts & 7,465.722 & 7,558.443 & 0.952 & 0.946 & 0.051 & 0.051\\
residuals & 7,465.986 & 7,537.635 & 0.930 & 0.939 & 0.054 & 0.065\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,382.013 & 7,445.232 & 0.997 & 0.995 & 0.016 & 0.018\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,602.905 & 3,655.727 & 1.000 & 1.013 & 0.000 & 0.023\\
Configural & 7,368.654 & 7,495.092 & 0.992 & 0.983 & 0.028 & 0.027\\
loadings & 7,364.904 & 7,474.483 & 0.990 & 0.986 & 0.025 & 0.036\\
intercepts & 7,358.503 & 7,451.224 & 1.000 & 1.001 & 0.000 & 0.037\\
residuals & 7,385.958 & 7,457.607 & 0.864 & 0.881 & 0.075 & 0.098\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,300.856 & 7,364.075 & 0.998 & 0.995 & 0.015 & 0.018\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,453.099 & 3,505.921 & 0.954 & 0.908 & 0.069 & 0.035\\
Configural & 7,218.848 & 7,345.287 & 0.965 & 0.929 & 0.059 & 0.033\\
loadings & 7,217.332 & 7,326.912 & 0.955 & 0.935 & 0.056 & 0.045\\
intercepts & 7,211.566 & 7,304.287 & 0.962 & 0.958 & 0.046 & 0.047\\
residuals & 7,304.566 & 7,376.215 & 0.562 & 0.619 & 0.137 & 0.189\\
\bottomrule
\end{tabular}

@@

\hypertarget{simulated-parital-invariance-results}{%
\subsection{Simulated Parital Invariance Results}\label{simulated-parital-invariance-results}}

@@

\hypertarget{invariance-plots-difference-scores-by-condition}{%
\subsection{Invariance Plots Difference Scores by Condition}\label{invariance-plots-difference-scores-by-condition}}

@@

\hypertarget{invariance-plots-effect-sizes-by-condition}{%
\subsection{Invariance Plots Effect Sizes by Condition}\label{invariance-plots-effect-sizes-by-condition}}

@@

\hypertarget{density-plots-by-condition}{%
\subsection{Density Plots by Condition}\label{density-plots-by-condition}}

>>>>

The outputs from this function are several \emph{ggplot2} objects that can be edited or saved directly using \emph{ggplot2} functionality (Wickham, 2016).

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  \texttt{saved\_configural}: a saved fitted model at the configural level with no equality constraints. This model should include all other lavaan settings you would like to use, such as estimator or ordered.
\item
  \texttt{data}: The dataframe where the model was estimated.
\item
  \texttt{model}: The model syntax for the overall model.
\item
  \texttt{group}: The grouping variable column in the dataframe.
\item
  \texttt{nboot}: The number of bootstraps to run.
\item
  \texttt{invariance\_index}: The fit index you would like to use to determine invariance. Please use options and labeling from \emph{lavaan} - see \texttt{fitmeasures()} for options.
\item
  \texttt{invariance\_rule}: The invariance difference score you would like to use as your rule.
\item
  \texttt{group.equal}: The equality constraints including in your original multi-group tests.
\end{enumerate}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 126,722.491 & 126,888.707 & 0.934 & 0.923 & 0.094 & 0.036\\
Group Clinical & 52,961.421 & 53,099.720 & 0.919 & 0.904 & 0.090 & 0.044\\
Group Student & 69,100.985 & 69,254.310 & 0.928 & 0.915 & 0.108 & 0.035\\
Configural & 122,118.406 & 122,617.055 & 0.926 & 0.912 & 0.102 & 0.036\\
Loadings & 122,144.532 & 122,566.010 & 0.925 & 0.918 & 0.098 & 0.043\\
Intercepts & 122,544.109 & 122,888.415 & 0.911 & 0.910 & 0.103 & 0.052\\
Residuals & 126,466.241 & 126,727.438 & 0.780 & 0.793 & 0.156 & 0.086\\
\bottomrule
\end{tabular}

@@

By examining our estimates, we can see that item seven on the RS-14 is estimated at nearly 5 points for the clinical sample, while the student sample has a lower mean around 4.5 points. Generally, students show higher means on the items of the RS-14, but when all loadings and other intercepts are constrained to be equal, and this one item is relaxed, this pattern flips so that clinical groups show higher item intercepts. Given the scale is a 1-7 Likert type scale, .5 a point represents a potentially sizable change on the scale. Item seven covers perseverance after hardship, and all items can be found in the user manual for the scale at www.resiliencecenter.com. The effect size from \(d_{MACS}\) suggests a small to medium effect, 0.28. In this next code section, we repeat this process for the RS6, as the CFI for our model with only RS7 does not achieve the levels of partial invariance for our \(\Delta\)CFI criterion (i.e., \textless= .01 downward change in fit: metric CFI = .925, partial scalar CFI = .914). See Figure \ref{fig:rs7-img} for the difference between item intercepts and latent means.

@@

Next, we would examine the strength of the effects of replication on each parameter at the intercept level. By examining Table \ref{tab:table-boot-effects}, it is clear that most of the item means are unlikely to replicate, even though two particular items can be used to create partial invariance. Figures \ref{fig:rs-partial-pic} and \ref{fig:rs-partial-pic2} display the three plots provided in the \texttt{bootstrap\_partial()} function. In general, we should expect \(M_{D}\) = 0.23 when items are invariant and \(M_{D}\) = 0.26 when items are not invariant. The effect size of non-invariant items ranges from 0.43 to 0.62.

@@

\begin{tabular}{lllll}
\toprule
Term & Non-Invariant & Random Non-Invariant & $h_{nmi}$ & $h_{nmi_p}$\\
\midrule
RS  Intercept & 0.991 & 0.007 & 2.784 & 0.886\\
RS1  Intercept & 0.989 & 0.007 & 2.764 & 0.880\\
RS10  Intercept & 0.988 & 0.007 & 2.755 & 0.877\\
RS11  Intercept & 0.991 & 0.007 & 2.784 & 0.886\\
RS12  Intercept & 0.991 & 0.007 & 2.784 & 0.886\\
RS13  Intercept & 0.991 & 0.007 & 2.784 & 0.886\\
RS14  Intercept & 0.990 & 0.007 & 2.774 & 0.883\\
RS2  Intercept & 0.985 & 0.007 & 2.728 & 0.869\\
RS3  Intercept & 0.988 & 0.007 & 2.755 & 0.877\\
RS4  Intercept & 0.990 & 0.007 & 2.774 & 0.883\\
RS5  Intercept & 0.984 & 0.007 & 2.720 & 0.866\\
RS6  Intercept & 0.979 & 0.007 & 2.683 & 0.854\\
RS7  Intercept & 0.974 & 0.007 & 2.650 & 0.844\\
RS8  Intercept & 0.991 & 0.007 & 2.784 & 0.886\\
RS9  Intercept & 0.987 & 0.007 & 2.746 & 0.874\\
\bottomrule
\end{tabular}

@@

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/rs-partial-pic-1.pdf}
\caption{\label{fig:rs-partial-pic}RS-14 scale invariance for item intercepts. The left panel indicates the raw score difference between groups and items, while the right panel indicates the effect size for group differences based on invariance.}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/rs-partial-pic2-1.pdf}
\caption{\label{fig:rs-partial-pic2}RS-14 scale invariance density plots, illustrating invariant versus non-invariant bootstrapped and random runs for each parameter.}
\end{figure}

@@

\hypertarget{simulating-from-models}{%
\section{Simulating from models}\label{simulating-from-models}}

@@

\hypertarget{simulating-from-matrices}{%
\section{Simulating from matrices}\label{simulating-from-matrices}}

@@

\hypertarget{mgcfa-model-fit-statistics}{%
\section{MGCFA Model Fit Statistics}\label{mgcfa-model-fit-statistics}}

Model fit statistics are provided for each of the ten model combinations (invariant, three sizes for each loadings, intercepts, and residuals). These tables could be used to examine the traditional change in fit statistics cutoff rules of thumb (Cheung \& Rensvold, 2002), such as \(\Delta\) CFI or \(\Delta\) RMSEA, to the visualizations presented in the manuscript.

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,516.454 & 7,579.673 & 1.000 & 1.036 & 0.000 & 0.006\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,767.599 & 3,820.421 & 1.000 & 1.008 & 0.000 & 0.021\\
Configural & 7,533.348 & 7,659.786 & 0.991 & 0.982 & 0.030 & 0.026\\
Loadings & 7,528.476 & 7,638.056 & 0.994 & 0.992 & 0.020 & 0.033\\
Intercepts & 7,522.397 & 7,615.118 & 1.000 & 1.003 & 0.000 & 0.035\\
Residuals & 7,520.435 & 7,592.083 & 0.991 & 0.992 & 0.020 & 0.046\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,530.321 & 7,593.540 & 0.977 & 0.955 & 0.049 & 0.025\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,785.242 & 3,838.064 & 0.979 & 0.958 & 0.050 & 0.029\\
Configural & 7,550.991 & 7,677.430 & 0.978 & 0.956 & 0.048 & 0.030\\
Loadings & 7,550.133 & 7,659.713 & 0.966 & 0.952 & 0.051 & 0.047\\
Intercepts & 7,542.675 & 7,635.397 & 0.979 & 0.977 & 0.035 & 0.047\\
Residuals & 7,534.091 & 7,605.739 & 0.993 & 0.994 & 0.019 & 0.054\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,598.681 & 7,661.900 & 0.946 & 0.893 & 0.078 & 0.035\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,820.090 & 3,872.912 & 0.969 & 0.938 & 0.067 & 0.034\\
Configural & 7,585.839 & 7,712.277 & 0.972 & 0.944 & 0.058 & 0.033\\
Loadings & 7,613.434 & 7,723.014 & 0.865 & 0.807 & 0.107 & 0.079\\
Intercepts & 7,606.648 & 7,699.370 & 0.874 & 0.860 & 0.091 & 0.079\\
Residuals & 7,600.057 & 7,671.705 & 0.880 & 0.895 & 0.079 & 0.091\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,684.982 & 7,748.201 & 0.987 & 0.973 & 0.040 & 0.023\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,857.143 & 3,909.965 & 0.992 & 0.984 & 0.037 & 0.029\\
Configural & 7,622.892 & 7,749.330 & 0.986 & 0.972 & 0.042 & 0.030\\
Loadings & 7,674.188 & 7,783.767 & 0.817 & 0.738 & 0.131 & 0.095\\
Intercepts & 7,667.682 & 7,760.403 & 0.824 & 0.805 & 0.113 & 0.096\\
Residuals & 7,683.177 & 7,754.825 & 0.762 & 0.793 & 0.116 & 0.138\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,520.471 & 7,583.690 & 1.000 & 1.035 & 0.000 & 0.007\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,767.599 & 3,820.421 & 1.000 & 1.008 & 0.000 & 0.021\\
Configural & 7,533.348 & 7,659.786 & 0.991 & 0.982 & 0.030 & 0.026\\
Loadings & 7,528.476 & 7,638.056 & 0.994 & 0.992 & 0.020 & 0.033\\
Intercepts & 7,526.312 & 7,619.034 & 0.987 & 0.986 & 0.027 & 0.040\\
Residuals & 7,524.356 & 7,596.005 & 0.975 & 0.978 & 0.033 & 0.050\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,538.375 & 7,601.594 & 1.000 & 1.033 & 0.000 & 0.008\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,767.599 & 3,820.421 & 1.000 & 1.008 & 0.000 & 0.021\\
Configural & 7,533.348 & 7,659.786 & 0.991 & 0.982 & 0.030 & 0.026\\
Loadings & 7,528.476 & 7,638.056 & 0.994 & 0.992 & 0.020 & 0.033\\
Intercepts & 7,544.002 & 7,636.724 & 0.917 & 0.907 & 0.068 & 0.059\\
Residuals & 7,542.064 & 7,613.712 & 0.905 & 0.917 & 0.065 & 0.067\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,568.748 & 7,631.967 & 1.000 & 1.032 & 0.000 & 0.008\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,767.599 & 3,820.421 & 1.000 & 1.008 & 0.000 & 0.021\\
Configural & 7,533.348 & 7,659.786 & 0.991 & 0.982 & 0.030 & 0.026\\
Loadings & 7,528.476 & 7,638.056 & 0.994 & 0.992 & 0.020 & 0.033\\
Intercepts & 7,574.054 & 7,666.776 & 0.797 & 0.775 & 0.106 & 0.084\\
Residuals & 7,572.174 & 7,643.823 & 0.785 & 0.813 & 0.097 & 0.090\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,462.007 & 7,525.226 & 1.000 & 1.020 & 0.000 & 0.013\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,703.797 & 3,756.619 & 0.962 & 0.924 & 0.061 & 0.037\\
Configural & 7,469.546 & 7,595.984 & 0.969 & 0.938 & 0.054 & 0.034\\
Loadings & 7,471.637 & 7,581.217 & 0.944 & 0.920 & 0.062 & 0.049\\
Intercepts & 7,465.722 & 7,558.443 & 0.952 & 0.946 & 0.051 & 0.051\\
Residuals & 7,465.986 & 7,537.635 & 0.930 & 0.939 & 0.054 & 0.065\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,382.013 & 7,445.232 & 0.997 & 0.995 & 0.016 & 0.018\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,602.905 & 3,655.727 & 1.000 & 1.013 & 0.000 & 0.023\\
Configural & 7,368.654 & 7,495.092 & 0.992 & 0.983 & 0.028 & 0.027\\
Loadings & 7,364.904 & 7,474.483 & 0.990 & 0.986 & 0.025 & 0.036\\
Intercepts & 7,358.503 & 7,451.224 & 1.000 & 1.001 & 0.000 & 0.037\\
Residuals & 7,385.958 & 7,457.607 & 0.864 & 0.881 & 0.075 & 0.098\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllll}
\toprule
Model & AIC & BIC & CFI & TLI & RMSEA & SRMR\\
\midrule
Overall & 7,300.856 & 7,364.075 & 0.998 & 0.995 & 0.015 & 0.018\\
Group Group 1 & 3,765.749 & 3,818.571 & 0.976 & 0.953 & 0.047 & 0.031\\
Group Group 2 & 3,453.099 & 3,505.921 & 0.954 & 0.908 & 0.069 & 0.035\\
Configural & 7,218.848 & 7,345.287 & 0.965 & 0.929 & 0.059 & 0.033\\
Loadings & 7,217.332 & 7,326.912 & 0.955 & 0.935 & 0.056 & 0.045\\
Intercepts & 7,211.566 & 7,304.287 & 0.962 & 0.958 & 0.046 & 0.047\\
Residuals & 7,304.566 & 7,376.215 & 0.562 & 0.619 & 0.137 & 0.189\\
\bottomrule
\end{tabular}

@@

\hypertarget{simulated-partial-invariance-results}{%
\section{Simulated Partial Invariance Results}\label{simulated-partial-invariance-results}}

@@

\hypertarget{invariance-plots-difference-scores-by-condition}{%
\section{Invariance Plots Difference Scores by Condition}\label{invariance-plots-difference-scores-by-condition}}

@@

\hypertarget{invariance-plots-effect-sizes-by-condition}{%
\section{Invariance Plots Effect Sizes by Condition}\label{invariance-plots-effect-sizes-by-condition}}

@@

\hypertarget{density-plots-by-condition}{%
\section{Density Plots by Condition}\label{density-plots-by-condition}}
